NLIZE: A Perturbation-Driven Visual Interrogation Tool for Analyzing and Interpreting Natural Language Inference Models

### 2018-07-23 paper/paper_entailVis.tex
fit into the limit

%% indicate IEEE Member or Student Member in form indicated below
 \author{Shusen Liu, Zhimin Li, Tao Li, Vivek Srikumar, Valerio Pascucci, Peer-Timo Bremer}
 \authorfooter{
 \vspace{-2mm}
% %% insert punctuation at end of each item
 \item
  Shusen Liu, Peer-Timo Bremer is with Lawrence Livermore National Laboratory. E-mail: \{liu42, bremer5\}@llnl.gov.
 \item
  Zhimin Li, Valerio Pascucci is with SCI Institute, University of Utah. E-mail: \{zhiminl, pascucci\}@sci.utah.edu.
  Tao Li, Vivek Srikumar is with School of Computing, University of Utah, E-mail:\{tli,svivek\}@cs.utah.edu
}

@@

%% if specified like this the section will be committed in review mode
\acknowledgments{
This work was performed under the auspices of the U.S. Department of Energy by Lawrence Livermore National Laboratory under Contract DE-AC52-07NA27344. This work is also supported in part by NSF: CGV: Award:1314896, NSF:IIP Award :1602127 NSF:ACI:award 1649923, DOE/SciDAC DESC0007446, CCMSC DE-NA0002375, and PIPER: ER26142 DE-SC0010498. This material is based upon work supported by the Department of Energy, National Nuclear Security Administration, under Award Number(s) DE-NA0002375. }

>>>>

%% indicate IEEE Member or Student Member in form indicated below
 \author{Shusen Liu, Zhimin Li, Tao Li, Vivek Srikumar, Valerio Pascucci and Peer-Timo Bremer}
 \authorfooter{
 \vspace{-2mm}
% %% insert punctuation at end of each item
 \item
  Shusen Liu, Peer-Timo Bremer is with Lawrence Livermore National Laboratory. E-mail: \{liu42, bremer5\}@llnl.gov.
 \item
  Zhimin Li, Valerio Pascucci is with SCI Institute, University of Utah. E-mail: \{zhimin, pascucci\}@sci.utah.edu.
  Tao Li, Vivek Srikumar is with School of Computing, University of Utah, E-mail:\{tli,svivek\}@cs.utah.edu
}

@@

%% if specified like this the section will be committed in review mode
\acknowledgments{
This work was performed under the auspices of the U.S. Department of Energy by Lawrence Livermore National Laboratory under Contract DE-AC52-07NA27344. This work is also supported in part by NSF: CGV: Award:1314896, NSF:IIP Award :1602127 NSF:ACI:award 1649923, DOE/SciDAC DESC0007446, CCMSC DE-NA0002375, PIPER: ER26142 DE-SC0010498, and NVIDIA Corporation. This material is based upon work supported by the Department of Energy, National Nuclear Security Administration, under Award Number(s) DE-NA0002375. }
